\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc\
\usepackage{enumitem}
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage[maxcitenames=6, minnames=3 ]{biblatex}
\addbibresource[]{biblio.bib}

% bold the name of specific author
\usepackage{xstring}
\usepackage{etoolbox}
\newboolean{bold}
\newcommand{\makeauthorsbold}[1]{%
  \DeclareNameFormat{author}{%
  \setboolean{bold}{false}%
    \renewcommand{\do}[1]{\expandafter\ifstrequal\expandafter{\namepartfamily}{####1}{\setboolean{bold}{true}}{}}%
    \docsvlist{#1}%
    \ifthenelse{\value{listcount}=1}
    {%
      {\expandafter\ifthenelse{\boolean{bold}}{\mkbibbold{\namepartfamily\addcomma\addspace \namepartgiveni}}{\namepartfamily\addcomma\addspace \namepartgiveni}}%
    }{\ifnumless{\value{listcount}}{\value{liststop}}
      {\expandafter\ifthenelse{\boolean{bold}}{\mkbibbold{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni}}{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni}}%
      {\expandafter\ifthenelse{\boolean{bold}}{\mkbibbold{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni\addcomma\isdot}}{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni\addcomma\isdot}}%
      }
    \ifthenelse{\value{listcount}<\value{liststop}}
    {\addcomma\space}{}
  }
}
\makeauthorsbold{Song, Taesoo}

% what is your name?
\newcommand{\myname}{Taesoo Song}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{20pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{10pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{2.5cm}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}
 
% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.3}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0.5em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{
    leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {Deep Learning, Machine Learning, Smart Meter ,Social Computation},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    % \nobibliography*
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Department of City and Regional Planning\\
        University of California, Berkeley
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:taesoo.song@berkeley.edu}{taesoo.song@berkeley.edu} \\
        \href{https://taesoosong.github.io}{taesoosong.github.io}\\
        % +1 575 418 0064 \\
        \href{https://scholar.google.com/citations?user=xM5Rc-EAAAAJ&hl=en}{Google Scholar}\\
        \href{https://orcid.org/0000-0002-0504-6353}{orcid: 0000-0002-0504-6353}
    \end{minipage}

    \section*{Education}
    
    \begin{tablist}
      \item[Ph.D.] \tab{}City and Regional Planning, \textbf{University of California, Berkeley}, USA, 2021-
      \begin{itemize}
        \item Dissertation: Reassessing Asian American Exceptionalism in Housing and the Role of Policy and Planning
        \vspace{-0.25em}
        \item Committee: Carolina Reid, Karen Chapple (co-chairs), Irene Bloemraad, Daniel Chatman
    \end{itemize}
      \item[M.S.] \tab{}Urban Planning and Engineering, \textbf{Yonsei University}, Seoul, South Korea, 2017-2019
      \begin{itemize}
        \item Thesis: Three Essays on the Impact of Community Contextual Characteristics on Resident Perceptions
    \end{itemize}
      \item[B.A.] \tab{}Economics, \textbf{Yonsei University}, Seoul, South Korea, 2012-2017
      \begin{itemize}
        \item Graduated with the Highest Honors
    \end{itemize}
    \end{tablist}
    
    \section*{Research Areas}
      Housing Policy, Neighborhood Change, Residential Mobility, Urban Inequality, Immigration\\
      Quantitative and Computational Methods, Urban Data Analytics
  
    \section*{Publications}
    \subsection*{In Progress}
    \begin{tablist}
        \item[Submitted] \tab{}Ramiller A., \textbf{Song, T.}, Parker, M. \& Chapple, K. "Residential Mobility and Big Data: Assessing the Validity of Consumer Reference Datasets."
        \item[Manuscript] \tab{}\textbf{Song, T.} "Affordability for Whom? The Impacts of Foreign Buyer Taxes on British Columbia and Ontario Rental Housing Markets."
        \end{tablist}
    \subsection*{Peer-reviewed Journal Articles}
    \begin{tablist}
        \item[In Press] \tab{}\textbf{Song, T.} \& Chapple, K. (In press). "Does Gentrification Constrain Housing Markets for Low-income Households? Evidence from Household Residential Mobility in the New York and San Francisco Metropolitan Areas." \emph{Urban Studies}.
        \item[2024] \tab{}Chapple, K. \& \textbf{Song, T.} \href{https://doi.org/10.1080/01944363.2024.2319293}{"Can New Housing Supply Mitigate Displacement and Exclusion? Evidence from Los Angeles and San Francisco."} \emph{Journal of the American Planning Association}, 1-15.
        \item[2022] \tab{}Lee, S., \textbf{Song, T.} \& Lim, U. \href{https://doi.org/10.1016/j.cities.2022.103768}{"How are Happy and Unhappy People Differently Affected by Their Local Environments? The Heterogeneous Relationship Between Happiness and Local Environments in Seoul, Korea."} \emph{Cities 127}, 103768.
        \item[2021] \tab{}Lee, S., \textbf{Song, T.} \& Lim, U. (2021). \href{https://www.dbpia.co.kr/Journal/articleDetail?nodeId=NODE11025769}{Wage Premium of Korean-Chinese Immigrant Workers in the Seoul Metropolitan Labor Market.} \emph{GRI Review 23}(3), 191-214 (in Korean).
        \item[2021] \tab{}\textbf{Song, T.} \& Lim, U. \href{https://www.mdpi.com/2071-1050/13/6/3441}{"The Effects of Mobility Expectation on Community Attachment: A Multilevel Model Approach."} \emph{Sustainability 13}(6), 3441.
        \item[2020] \tab{}\textbf{Song, T.} \& Lim, U. \href{"https://www.koreascience.or.kr/article/JAKO202030161655441.page}{"The Multilevel Effects of Regional Deprivation on Perceived Upward Social Mobility of Residents."} \emph{Journal of the Korean Regional Science Association 36}(3), 1-1[4] (in Korean).
    \end{tablist}
    \subsection*{Book Chapter}
    \begin{tablist}
        \item[2020] \tab{}\textbf{Song, T.} "Queering Seoul through the Lens of Urban Planning." In Seoul Queer Collective (Ed.), \emph{\href{http://www.kyobobook.co.kr/product/detailViewKor.laf?ejkGb=KOR&mallGb=KOR&barcode=9791197096501}{Jongno 3-ga Taja, Taja Jongno 3-ga [Others, Jongno 3-ga]}}. (pp. 53-81). Seoul: Seoul Queer Collective Press (in Korean).
    \end{tablist}
    \subsection*{Policy Reports}
    \begin{tablist}
        \item[2021] \tab{}Oh, E., Kim, S. \& \textbf{Song, T.} \emph{\href{http://global.si.re.kr/content/current-changes-and-challenges-seoul-webtoon-industry-and-policy-agendas}{Current Changes and Challenges of Seoul Webtoon Industry and Policy Agendas.}} The Seoul Institute (in Korean).Seoul: Seoul Queer Collective Press (in Korean).
        \item[2020] \tab{}Oh, E., Kim, M., Choi, B., \textbf{Song, T.}, Yoon, J., Jung, H. \& Hwang, M. \emph{A Research Report on the Development Strategies for Seoul Historic Downtown Specialized Industries.} Seoul Metropolitan Government (in Korean).
    \end{tablist}
    
    \section*{Talks}
    \subsection*{Conference Papers Presented}
    \begin{tablist}
      \item[2024] \tab{}\textbf{Song, T.} \& Chapple, K. "Does Gentrification Constrain Housing Markets for Low-income Households? Evidence from Household Residential Mobility in the New York and San Francisco Metropolitan Areas." \emph{52nd International Conference on Urban Affairs}, New York, NY.
      \item[2023] \tab{}\textbf{Song, T.} "Affordability for Whom? The Impacts of Foreign Buyer Taxes on British Columbia and Ontario Rental Housing Markets." \emph{The Association of Collegiate Schools of Planning 2023 Annual Conference}, Chicago, IL.
      \item[2022] \tab{}\textbf{Song, T.} \& Chapple, K. "Does Gentrification Constrain Housing Markets for Low-income Households? Evidence from Household Residential Mobility in the New York and San Francisco Metropolitan Areas." \emph{The Association of Collegiate Schools of Planning 2022 Annual Conference}, Toronto, ON.
      \item[2019] \tab{}\textbf{Song, T.} \& Lim, U. "Does Contact Breed Tolerance? Community Socioeconomic Status and Established Residents' Opposition to Local Public Housing Provision." \emph{The 15th International Congress of Asian Planning Schools Association}, Seoul, South Korea.
      \item[2018] \tab{}\textbf{Song, T.} \& Lim, U.  "Do Locational Stability and Housing Tenure Affect Residents' Community Attachment?." \emph{Korea Planning Association 2018 Fall Conference}, Daegu, South Korea.
      \item[2018] \tab{}\textbf{Song, T.}, Kim, J. \& Lim, U. "Deprived Districts, Deprived Aspirations for the Future? The Impact of Regional Deprivation on Perceived Prospects of Upward Mobility." \emph{Korea Planning Association 2018 Spring Conference}, Seoul, South Korea.
        \item[2018] \tab{}\textbf{Song, T.} \& Lim, U. "What Makes Neighbors Trust Each Other? A Comparative Analysis Based on Housing Types." \emph{48th International Conference on Urban Affairs}, Toronto, ON.
    \end{tablist}
    \subsection*{Invited Talks}
    \begin{tablist}
    \item[2022] \tab{}Korea Development Institute. "Analyzing Urban Displacement Through Spatial Data Analysis." Nov. 16
    \end{tablist}
    \subsection*{Campus Talks}
    \begin{tablist}
        \item[2024] \tab{} Associated Students of the University of California (ASUC) Housing Commission, UC Berkeley. Housing Professionals Panel. Apr. 4
        \item[2023] \tab{} Canadian Studies Program, UC Berkeley. "Affordability for Whom? The Impacts of Foreign Buyer Taxes on British Columbia and Ontario Rental Housing Markets." Apr. 26
    \end{tablist}

% \section*{INVITED TALKS}
    % \subsection*{Campus Talks}

\section*{Awards}
    \subsection*{Grants and Fellowship}
    \begin{tablist}
        \item[2022] \tab{}Edward E. Hildebrand Research Fellowship, UC Berkeley Canadian Studies Program
        \item[2022] \tab{}Summer Research Funding, UC Berkeley Global Metropolitan Studies
        \item[2021-2026] \tab{}Doctoral Study Abroad Fellowship, Korea Foundation for Advanced Studies
        \item[2020] \tab{}Fulbright Graduate Student Program Candidate (Declined), Fulbright Korea
        \item[2017-2018] \tab{}Yonsei Outstanding Graduate Student Scholarship, Yonsei University
    \end{tablist}
    \subsection*{Awards and Honors}
    \begin{tablist}
        \item[2022] \tab{}Graduate Assembly Professional Development Award, UC Berkeley
        \item[2017] \tab{}Graduated with the Highest Honors, Yonsei University
        \item[2017] \tab{}Best Paper in History, Yonsei University Underwood Int'l College
        \item[2015-2017] \tab{}High Honors, Yonsei University
    \end{tablist}

  \section*{Service}
  \subsection*{University of California, Berkeley}
    \begin{tablist}
        \item[2024] \tab{}City and Regional Planning PhD Admissions Committee
        \item[2023] \tab{}Faculty Search Doctoral Student Lead (Land and Housing Economics)
    \end{tablist}
  \subsection*{Membership}
    \begin{tablist}
        \item[2023-Present] \tab{}Urban Affairs Association
        \item[2022-Present] \tab{}Association of Collegiate Schools of Planning
    \end{tablist}
    \subsection*{Reviewer}
    Berkeley Planning Journal, Regional Studies

    \section*{Research Positions}
    \begin{tablist}
        \item[2023-Present] \tab{}Graduate Student Researcher at \href{https://ternercenter.berkeley.edu/}{\textbf{Terner Center for Housing Innovation}}
        \item[2023-Present] \tab{}Policy Reporter at \href{si.re.kr}{\textbf{Seoul Institute}}
        \item[2021-2023] \tab{}Graduate Student Researcher at \href{https://www.urbandisplacement.org/}{\textbf{Urban Displacement Project}}
        \item[2019-2021] \tab{}Researcher at \href{si.re.kr}{\textbf{Seoul Institute}}
    \end{tablist}

 \section*{Teaching}
    \subsection*{University of California, Berkeley (Lead Instructor)}
    \begin{tablist}
        \item[2024 Summer] \tab{}CYPLAN 130 U.S. Housing, Planning, and Policy
        \item[2023 Summer] \tab{}CYPLAN 101 Introduction to Urban Data Analytics
    \end{tablist}
    \subsection*{Yonsei University (Teaching Assistant)}
    \begin{tablist}
      \item[2019 Spring] \tab{}UIC1551 World History: Group II
      \item[2018-2019] \tab{}UIC1501 World History: Group I 
      \item[2018 Spring] \tab{}CRP3610 Urban and Regional Economics
      \item[2017 Fall] \tab{}CRP2350 National and Regional Planning
    \end{tablist}

  
\end{document}
